
\section{Technologies Used}

\subsection{Near Field Communication}
Near Field Communication(NFC) is the set of protocols that enable electronic devices to establish radio communication with each other by touching the devices together, or bringing them into proximity to a distance of typically 10cm or less.
Unsolvable Solutions have decided to use this technology for the following reasons:
\\The reasons for using this technology are:
\begin{itemize}
\item Client requirement specification
\item This method is more secure than other communication methods, because it requires the devices communicating to be less than 10cm apart. This enables one to monitor the users that communicate via NFC.
%\item It is convenient because the user have
\end{itemize}


\subsection{ Node.js}
Node.js is an open-source, cross-platform runtime environment for developing server-side web applications. Node.js applications are written in JavaScript. 
\\The reasons for using this technology are:
\begin{itemize}
\item It works well with MongoDB
\item Personal preference.
\end{itemize}

\subsection{ Arduino}Arduino is an open-source computer hardware and software company, project and user community that designs and manufactures microcontroller-based kits for building digital devices and interactive objects that can sense and control the physical world.
\\The reasons for using this technology are:
\begin{itemize}
\item Supports NFC
\end{itemize}

\subsection{MongoDB}
MongoDB is an open source, document-oriented database designed with both scalability and developer agility in mind. Instead of storing your data in tables and rows as you would with a relational database, in MongoDB you store JSON-like documents with dynamic schemas.
\\The reasons for using this technology are:
\begin{itemize}
\item It has fast processing.
\item Open source.
\item Previous knowledge.
\item Personal preference.
\item Flexibility.
\end{itemize}

%\subsection{Passport}


\subsection{Java}
Java is a programming language expressly designed for use in the distributed environment of the Internet. It was designed to have the "look and feel" of the C++ language, but it is simpler to use than C++ and enforces an object-oriented programming model.
\\It is used in conjuction with Angroid SDK.


\subsection{Android SDK}
A software development kit that enables developers to create applications for the Android platform. The Android SDK includes sample projects with source code, development tools, an emulator, and required libraries to build Android applications.
\\The reason for using this technology are:
\begin{itemize}
\item All application created for Android need to be done through the Android SDK.
\end{itemize}

\subsection{Host Card Emulation}
Host Card Emulation (HCE) is the term describing on-device technology that permits a phone to perform card emulation on an Near Field Communication (NFC)-enabled device without relying on access to a secure element
\\The reasons for using this technology are:
\begin{itemize}
\item In order for an Android device to send a data via NFC to a non-Android device, we needed to emulate a NFC tag. HCE allows us to emulate a universal NFC tag that is readable by almost any device that can process NFC messages.

\end{itemize}
%\subsection{INDEF}

\subsection{JavaScript}
JavaScript is most commonly used as a client side scripting language. This means that JavaScript code is written into an HTML page. When a user requests an HTML page with JavaScript in it, the script is sent to the browser and it's up to the browser to do something with it.
\\The reasons for using this technology are:
\begin{itemize}
\item It is easy to use with Node.js and MongoDB
\item It is freely available.
\item It is a very powerful and flexible language.
\end{itemize}

\subsection{AngularJS}

AngularJS is a structural framework for dynamic web apps. It lets you use HTML as your template language and lets you extend HTML's syntax to express your application's components clearly and succinctly. Angular's data binding and dependency injection eliminate much of the code you would otherwise have to write.
\\The reasons for using this technology are:
\begin{itemize}
\item It is easy to use with JavaScript, Node.js and MongoDB
\item It is freely available.
\item It is a very powerful and flexible language.
\end{itemize}

\subsection{Intel Edison}
The Intel Edison is a tiny computer offered by Intel as a development system for wearable devices. The system was initially announced to be the same size and shape as an SD card and contain a dual-core Intel Quark x86 CPU at 400 MHz communicating via Bluetooth and Wi-Fi.
\\The Intel Edison is used as the gateway. The reasons for using this technology are:
\begin{itemize}
\item The two options for the gateway was using the Intel Edison or using the a Raspberry Pi. And even though the Raspberry Pi was cheaper (R550), the Intel Edison( R1666) has built in wifi. 
\item The Intel Edison was sponsored by Intel for the project.
\end{itemize}